---
title: "Views on Foreign Policy: U.S. Adults"
subtitle: "From Wave 116 of the American Trends Panel"
author: "John Michaud, MA candidate in International Affairs"
institute: "American University, Washington D.C."
date: "2024-03-25"
output: 
  beamer_presentation: 
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center'
)

library(tidyverse)
library(haven)
library(ggplot2)
library(patchwork)

ATP_W116 <- read_sav("~/Desktop/Spring 2024/Data Analysis/09-presentations/ATP W116.sav")
```

## Data

* American Trends Panel 
  + online, nationally representative panel of American adults
  + created by the Pew Research Center and managed by IPSOS
  + asks questions on politics, public policy, and social issues



* Wave 116  
  + responses from 5,726 randomly-selected panelists
  + collected between Oct. 10 and Oct. 16, 2022 



* Analysis
  + check for partisan differences on foreign policy 
    + respondents grouped by variable DRLEAD 
  + two questions on U.S. foreign policy 
    + SUPERPWR
    + ALLIES
  


## Support for U.S. military supremacy across party lines

```{r, fig.dim = c(4,3)}
tab2 =
ATP_W116 |>
  count(DRLEAD_W116, SUPERPWR_W116) |>
  mutate(Superpower = factor(SUPERPWR_W116, 
                             levels = c("1", "2", "99"), ordered = TRUE),
         PartyPref = factor(DRLEAD_W116, 
                                        levels = c("1","2","3","99"), ordered = TRUE)) |>
  select(PartyPref, Superpower, n)

P3 =
tab2 |>
  filter(PartyPref != "99",
       Superpower != "99") |>
  ggplot(aes(fill = Superpower, y = n, x = PartyPref)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  theme(panel.background = element_rect(color = "black")) +
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank())

P_Superpower =
P3 +
  scale_fill_discrete(
    name = "In the future, do you think...",
    breaks = c("1", "2"),
    labels = c("U.S. policies should try to keep it so\nAmerica is the only military superpower (1)", 
               "It would be acceptable if another country\nbecame as militarily powerful as the U.S. (2)")) +
  theme(legend.position = c(.74, .835)) +
  theme(legend.spacing.y = unit(1, "mm")) +
  guides(fill = guide_legend(byrow = TRUE)) +
  scale_y_continuous(limits = c(0, 1500),
                     name = NULL) +
  scale_x_discrete(breaks = c("1", "2", "3"),
                   labels = c("Favors Republicans", "Favors Democrats", "Unsure"),
                   name = NULL) +
  labs(title = "All Respondents") +
  theme(
    axis.text = element_text(color = "black", size = 7),
    legend.text = element_text(color = "black", size = 5),
    legend.title = element_text(color = "black", size = 5.5),
    plot.title = element_text(hjust = .5),
    axis.ticks.x = element_blank()
  ) 


P_Superpower
```

```{r, include = FALSE}
tab = 
ATP_W116 |>
  count(DRLEAD_W116, ALLIES_W116) |>
  mutate(PartyPref = factor(DRLEAD_W116, 
                            levels = c("1","2","3","99"), ordered = TRUE),
         Allies = factor(ALLIES_W116,
                        levels = c("1", "2", "99"), ordered = TRUE)) |>
  select(PartyPref, Allies, n) 

tab1 = as.data.frame(tab)

P1 = 
tab1 |>
  filter(PartyPref != "99",
         Allies != "99") |> 
  ggplot(aes(fill = Allies, x = Allies, y = n)) +
  geom_bar(stat = "identity", width = 1) +
  theme_bw() +
  theme(panel.background = element_rect(color = "black")) +
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank()) +
  labs(title = "All Respondents", size = 7) +
  scale_fill_discrete(guide = FALSE) +
  scale_y_continuous(name = NULL) +
  scale_x_discrete(breaks = c("1", "2"),
                   labels = NULL,
                   name = NULL) +
  theme(
    axis.text = element_text(color = "black", size = 7),
    axis.title.x = element_text(color = "black", size = 7),
    axis.ticks.x = element_blank()
  )
  
new_labels <- c("1" = "R", "2" = "D", "3" = "U")

P2 = 
  P1 + facet_wrap(~ PartyPref, 
                  labeller = labeller(PartyPref = new_labels),
                  scales = 'free_y') +
  scale_x_discrete(breaks = c("1", "2"),
                   labels = NULL,
                   name = NULL) +
  theme(axis.title.x = element_text(color = "black", size = 7)) +
  scale_fill_discrete(guide = FALSE) +
  labs(title = "By Party Preference", size = 7)
  
P_Allies =
P1 + P2 +
  scale_fill_discrete(
    name = "The U.S...",
    breaks = c("1", "2"),
    labels = c("should take into account the interests of its\n allies even if it means making compromises (1)",
               "should follow its own national interests\neven when its allies strongly disagree (2)")
  ) +
  theme(
    legend.position = "bottom",
    legend.justification = c("right"),
    legend.title = element_text(color = "black", size = "6"),
    legend.text = element_text(color = "black", size = "5"),
    axis.ticks.x = element_blank()
  )
```


## Partisan differences on how U.S. should approach alliances 

```{r, fig.dim = c(4,3)}

P_Allies


```








